Make any stupid plot you want

### 2021-02-08 draft/sections/intro.tex
prototype

@@

\begin{figure}
    \begin{subfigure}{.20\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_spinny.png}
        \caption{}
        \label{fig:intro_dpa}
    \end{subfigure}
    \begin{subfigure}{.20\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_bar.png}
        \caption{}
        \label{fig:intro_dpb}
    \end{subfigure}
    \begin{subfigure}{.20\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_country.png}
        \caption{}
        \label{fig:intro_dbc}
    \end{subfigure}
    \begin{subfigure}{.20\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_heat.png}
        \caption{}
        \label{fig:intro_dbd}
    \end{subfigure}
    \caption{Du Bois' data portraits\cite{duboiscenterattheuniversityofmassachusettsBoisDataPortraits2018} of post reconstruction Black American life exemplify that the fundemental characteristics of data visualization is that the visual elements vary in proportion to the source data. In figure~\ref{fig:intro_dpa}, the length of each segment maps to population; in figure~\ref{fig:intro_dpb}, the bar charts are intersected to show the number of property owners and how much they own in a given year; in figure~\ref{fig:intro_dpc} the countries are scaled to population size; and figure~\ref{fig:intro_dpd} is a treemap where the area of the rectangle is representative of the number of businesses in each field. The images here are from the Prints and Photographs collection of the Library of Congress \cite{duboisGeorgiaNegroCity1900, duboisGeorgiaNegroCity1900,duboisSeriesStatisticalCharts,duboisSeriesStatisticalChartsa}}
    \label{fig:intro_dubois}
\end{figure}

This work is motivated by a rearchitecture of the Matplotlib visualization library that aims to disentangle the transformation from data to visualization.

@@

For example, the Du Bois data portraits in figure~\ref{fig:intro_dubois} are not scatter plots or line plots or really maps, but are clearly identifiable as data visualizations because there are some properties of the original data they preserve.

@@

\subsection{ What are the the basic requirements of a visualization library?}
Acquired codes of meaning, dubois

@@

\subsection{contribution of this work is}
 % topological model (abstractions for continuity, formal definition of structure preservation as monoidal action equivarance)
 % prototype
\end{document}

>>>>

\begin{figure}
    \begin{subfigure}{.24\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_spinny.png}
        \caption{}
        \label{fig:intro_dpa}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_bar.png}
        \caption{}
        \label{fig:intro_dpb}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_country.png}
        \caption{}
        \label{fig:intro_dbc}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \includegraphics[width=1\textwidth]{figures/intro/du_bois_heat.png}
        \caption{}
        \label{fig:intro_dbd}
    \end{subfigure}
    \caption{Du Bois' data portraits\cite{duboiscenterattheuniversityofmassachusettsBoisDataPortraits2018} of post reconstruction Black American life exemplify that the fundemental characteristics of data visualization is that the visual elements vary in proportion to the source data. In figure~\ref{fig:intro_dpa}, the length of each segment maps to population; in figure~\ref{fig:intro_dpb}, the bar charts are intersected to show the number of property owners and how much they own in a given year; in figure~\ref{fig:intro_dpc} the countries are scaled to population size; and figure~\ref{fig:intro_dpd} is a treemap where the area of the rectangle is representative of the number of businesses in each field. The images here are from the Prints and Photographs collection of the Library of Congress \cite{duboisGeorgiaNegroCity1900, duboisGeorgiaNegroCity1900,duboisSeriesStatisticalCharts,duboisSeriesStatisticalChartsa}}
    \label{fig:intro_dubois}
\end{figure}

@@

@@

Intuitively, data visualizations are drawings where elements of the figure are mapped 
For example, the Du Bois data portraits in figure~\ref{fig:intro_dubois} are not scatter plots or line plots or really maps, but are clearly identifiable as data visualizations because there are some properties of the original data they preserve.

@@

Acquired codes of meaning, dubois

@@

\subsection{contribution}
 % topological model (abstractions for continuity, formal definition of structure preservation as monoidal action equivarance)
 % prototype

\begin{enumerate}
    \item fiber bundle representation of data and graphics
    \item formalization of variable type structure preservation as monoid action equivariant maps between fibers 
    \item formalization of continuity preservation as equivariant map between base space
    \item algebraic sum for composition of graphics
    \item functional approach to force seperation of scope and concerns
    \item prototype  
\end{enumerate}

\end{document}
